 \documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm}
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amssymb,multicol}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{enumitem}
\usepackage{xcolor,systeme}

\newcommand{\Z}{\mathbb{Z}}
\newcommand{\ds}{\displaystyle}
\newtheorem*{theorem}{Theorem}

\newlist{checklist}{itemize}{2}
\setlist[checklist]{label=$\square$}

\begin{document}
\begin{center}
{\Large Homework 10}\\
Due: Friday,  April 28 at 11:59pm\\


\end{center}
{\bf Instructions:} Submit a pdf of your solutions to the HW 10 assignment on Gradescope.  

{ These problems will be graded for proficiency credit only.  You may do as many or as few of them as you would like.}



\begin{enumerate}
\item[0.] List the skill and the corresponding problem for each skill you would like to earn proficiency with. 

\item In this problem, you will explain why the square root attack on RSA works. Let $N=pq$, where $p$ and $q$ are prime numbers.  Let $a$ and $b$ be two integers such that $a\not\equiv \pm b\pmod{N}$.  Prove that, if $x>1$ is an integer such that $x|N$ and $x|a+b$, then $x=p$ or $x=q$. 

\item Without explicitly squaring any integers modulo $m$ for any integer $m$, determine if $2$ is a square modulo $35$. 

\item Let $p$ be an odd prime. How many integers $0\le x \le p-1$ satisfy the congruence $(x^p)^p-(x^{p-1})^p+x^{p-1}-x\equiv 0\pmod{p}?$ Explain your answer with a proof. 

\item Define $\gcd(a,b,c)$ to be the largest integer $d$ such that $d|a$, $d|b$, and $d|c$.  Let $a$, $b$, and $c$ be integers such that $\gcd(a,b,c)=1$. Prove that there are integers $w$, $x$, and $y$ such that $aw+bx+cy=1$.  (Note that it is possible in this problem to have $\gcd(a,b)>1$, $\gcd(b,c)>1$, and $\gcd(a,c)>1$.)

\item Show that there are no integers $x$, $y$, and $z$ such that $x^3+y^3+7z^4=3$. 

\end{enumerate}


\end{document}
