 \documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm}
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amssymb,multicol}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{enumitem}
\usepackage{xcolor,systeme}

\newcommand{\Z}{\mathbb{Z}}
\newtheorem*{theorem}{Theorem}

\newlist{checklist}{itemize}{2}
\setlist[checklist]{label=$\square$}

\begin{document}
\begin{center}
{\Large Homework 4}\\
Due: Friday,  February 24 at 11:59pm\\


\end{center}
{\bf Instructions:} Submit a pdf of your solutions to the HW 4 assignment on Gradescope. 



\begin{enumerate}
\item[0.] If you would like any of these problems to be graded for proficiency with the core skills, list the skill and the corresponding problem. 
\item Find all solutions to the linear congruence equation $$15x\equiv 6\pmod{9}$$ or explain why no solution exists.

\item Solve each of the following simultaneous systems of congruences or explain
why no solution exists.
\begin{enumerate}
\item $\systeme*{x\equiv 5\pmod{13}, x\equiv 2\pmod{7}\;\;, x\equiv 4 \pmod{11}}$
\item $\systeme*{x\equiv 3\pmod{9}, x\equiv 2\pmod 6, x\equiv 1\pmod{5}}$
\end{enumerate}

\item This exercise will help us work towards understanding square roots. 
\begin{enumerate}
\item Let $p$ be a prime number and let $b$ be an integer such that $x^2\equiv b\pmod{p}$ has a solution.  Show that,  if $a_1$ and $a_2$ are two such solutions, then $a_1\equiv a_2\pmod{p}$ or $a_1\equiv -a_2\pmod{p}$. 
\item Provide a counterexample to show that the above statement is not necessarily true if $p$ is not prime. In other words, provide integers $m$, $b$, $a_1$, and $a_2$ such that $a_1^2\equiv b\pmod{m}$, $a_2^2\equiv b\pmod{m}$, but $a_1\not \equiv \pm a_2 \pmod{m}$. Make sure you explain why your counterexample is, in fact, a counterexample. 
\end{enumerate}

\item Prove that $x^2+y^2=95$ has no integer solutions.

\end{enumerate}

\end{document}