   \documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm}
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amssymb,multicol}
\usepackage{hyperref, enumitem}
\usepackage{xcolor,graphicx}

\newcommand{\Z}{\mathbb{Z}}
\newtheorem*{theorem}{Theorem}

\newlist{checklist}{itemize}{2}
\setlist[checklist]{label=$\square$}

\begin{document}
\begin{center}
{\Large Homework 1}\\
Due: Friday,  February 6 at 11:59pm CST\\


\end{center}
{\bf Instructions:} Submit a pdf of your solutions to the HW 1 assignment on Gradescope. 

Problem 5 is marked as a peer review problem. \href{https://docs.google.com/document/d/1jSw9pmMJJFUx_6dTkcUi4k4HJNIrrIIgs9zdWhAycx0/edit?usp=drive_link}{This document} gives directions and deadlines for the peer review process.

When working on this assignment, you should focus on the following goals:
\begin{itemize}
\item Demonstrate that you understand the definition of reduction modulo $m$ and how it relates to the division algorithm. 
\item Clearly communicate computational solutions using complete sentences and enough explanation that another 5248 student could follow your work.
\item Clearly and correctly apply the definition of divisibility in a proof. 
\item Clearly and correctly apply the division algorithm in a proof.
\item Write clear and correct proofs that meet the following conventions of a mathematical proof:
\begin{checklist}
\item Written in complete sentences.
\item All assumptions stated at the beginning of the proof.
\item Define variables before/when you use them.
\item Use symbols when writing a precise mathematical formula or equation and English words when not writing a formula (i.e. do not use a symbol, such as $\forall,\, \exists,\, \therefore, \, \implies$ in place of a word or phrase.)
\item Show computational/algebraic work vertically and centered in the page. 
\end{checklist}
\end{itemize}

\begin{enumerate}
\item Compute the following reductions.  For parts (a) and (c), show your work without using any integers larger than 144. 
\begin{enumerate}

\item $(130\cdot 142) \% 3$ \\
\item $(-2000) \% 91$\\
\item $\left(3^{76}\right) \% 13$ 
\end{enumerate}
\item
\begin{enumerate}
\item  Let $N$ be an integer so that $N\%24 = 2$.  What is $N\%6$?  Prove that your answer is true for any integer $N$ such that $N\%24=2$.
\item Fix an integer $N$ such that $N\%6=2$. What are the possible values of $N\%24$? Explain your answer. 
\end{enumerate}

\item Suppose you know that the plaintext ``snow" has been encoded to the ciphertext ``JEFN" using a shift cipher.  You intercept the ciphertext ``NZEKVI," which you know has been encoded with the same shift cipher.  Decrypt the second message ``NZEKVI." Make sure to show your work.   What type of attack did you perform?

\item Let $a$, $b$, and $c$ be integers such that $a|b$ and $a|c$. Prove that,  for any integers $u$ and $v$, $a|ub+vc$. 
\item (Peer Review Problem) Let $m$ be any positive integer. Prove that  if $r$ is the reduction of $N$ modulo $m$ with $r\ne 0$, then $m-r$ is the reduction of $-N$ modulo $m$.  (Note: you likely have a lot of this problem completed from the in-class activity!)


\end{enumerate}

\end{document}
