   \documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm}
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amssymb,multicol}
\usepackage{hyperref, enumitem}
\usepackage{xcolor,graphicx}

\hypersetup{
    colorlinks=true}

\newcommand{\Z}{\mathbb{Z}}
\newtheorem*{theorem}{Theorem}

\newlist{checklist}{itemize}{2}
\setlist[checklist]{label=$\square$}

\begin{document}
\begin{center}
{\Large Homework 3}\\


\end{center}
{\bf Instructions:} Submit a pdf of your solutions to the HW 3 assignment on Gradescope by 11:59pm on Friday February 20. 

Problem 2 is marked as a peer review problem. \href{https://docs.google.com/document/d/1jSw9pmMJJFUx_6dTkcUi4k4HJNIrrIIgs9zdWhAycx0/edit?usp=drive_link}{This document} gives directions and deadlines for the peer review process.

When working on this assignment, you should focus on the following goals:
\begin{itemize}
\item Clearly communicate computational solutions using enough explanation that another 5248 student could follow your work.
\item Use Euclid's Lemma clearly and correctly in a proof.
\item Use Bezout's identity clearly and correctly in a proof. 
\item Demonstrate understanding of how to compute the index of coincidence.
\item Demonstrate understanding of how to use the Mutual Index of Coincidence to determine information about a Vigen\'ere Cipher Key.
\item Write clear and correct proofs that meet the following conventions of a mathematical proof:
\begin{checklist}
\item Written in complete sentences.
\item All assumptions stated at the beginning of the proof.
\item Define variables before/when you use them.
\item Use symbols when writing a precise mathematical formula or equation and English words when not writing a formula (i.e. do not use a symbol, such as $\forall,\, \exists,\, \therefore, \, \implies$ in place of a word or phrase.)
\item Show computational/algebraic work vertically and centered in the page. 
\end{checklist}
\end{itemize}

\begin{enumerate}
\item[0.] If you would like any of these problems to be graded for proficiency with the core skills, list the skill and the corresponding problem. 
\item Let $a,b,c$ be nonzero integers. Prove that if $a$ and $c$ are coprime and $b$ and $c$ are also coprime, then $ab$ and $c$ are coprime. (Hint: Use Bezout's Identity)
\item (Peer review problem) This exercise will help us work towards understanding square roots, which will come up later in the semester.  (Each part will be worth 4 points and graded as a separate problem.)
\begin{enumerate}

\item Let $p$ be a prime number and let $b$ be an integer such that $x^2\equiv b\pmod{p}$ has a solution.  Show that,  if $a_1$ and $a_2$ are two such solutions, then $a_1\equiv a_2\pmod{p}$ or $a_1\equiv -a_2\pmod{p}$. 
\item Provide a counterexample to show that the above statement is not necessarily true if $p$ is not prime. In other words, provide integers $m$, $b$, $a_1$, and $a_2$ such that $a_1^2\equiv b\pmod{m}$, $a_2^2\equiv b\pmod{m}$, but $a_1\not \equiv \pm a_2 \pmod{m}$. Make sure you explain why your counterexample is, in fact, a counterexample. 
\end{enumerate}
\item Consider an alphabet with four characters: $\spadesuit$, $\heartsuit$, $\diamondsuit$, and $\clubsuit$.  Suppose that you have a text $\underline{s}$ written in this alphabet which consists of $60$ $\spadesuit$s,  $14$ $\heartsuit$s, $20$ $\diamondsuit$s, and $6$ $\clubsuit$s.  What is $\textrm{IndCo}(\underline{s})$?
\item You are trying to attack a Vigenere cipher.  You have already determined that this Vigenere cipher has key length $4$.  If $\underline{s} = (s_1, \ldots, s_{N})$ is a string of ciphertext of length $N$ with $N \equiv 0 \pmod4$, let $s^{(j)} = (s_j,s_{4+j},s_{8+j},\ldots,s_{N-4+j})$ be the substring of $s$ whose typical entry is $s_i$ for some $i \equiv j \pmod 4$.  Let $E_t(s^{(j)})$ be the encryption of the string $s^{(j)}$ by the shift cipher with key $t$ for $0 \leq t \leq 25$ and $1 \leq j \leq 4$ (i.e. the string obtained by taking $s^{(j)}$ and shifting each character forward by $t$ letters).  You compute the following table:

\begin{center}
    \begin{tabular}{ l | l | l | l }
    $t$ & $\mathrm{MutIndCo}(s^{(1)},E_t(s^{{(2)}}))$ & $\mathrm{MutIndCo}(s^{(1)},E_t(s^{{(3)}}))$  & $\mathrm{MutIndCo}(s^{(1)},E_t(s^{{(4)}}))$  \\ \hline
    4 & 0.057 & 0.038 & 0.039 \\     
    5 & 0.042 & 0.041 & 0.054 \\ 
    7& 0.052 & 0.069 & 0.042\\ 
    12 & 0.064 & 0.058 & 0.039\\ 
    14 & 0.043 & 0.065 & 0.068 \\ 
    22 & 0.040 & 0.039 & 0.051
    \end{tabular}
      \begin{tabular}{ l | l | l}
    $t$ & $\mathrm{MutIndCo}(s^{(2)},E_t(s^{{(3)}}))$ & $\mathrm{MutIndCo}(s^{(2)},E_t(s^{{(4)}}))$\\ \hline
    3 & 0.044 & 0.041 \\     
    5 & 0.039 & 0.069\\ 
    8 & 0.051 & 0.038\\ 
    11 & 0.041 & 0.061\\ 
    16 & 0.045 & 0.052\\ 
    23 & 0.061 & 0.045\\
    \end{tabular}
    \end{center} 
    
For the questions below, assume that,  values of $t$ not appearing in the table above gave rise values of $\mathrm{MutIndCo}(s^{(j)},E_t(s^{(k)}))$ that are unremarkable for all $1 \leq j<k \leq 4$.  
\begin{enumerate}
\item Given that the key has the form $k = (k_1, k_2 k_3,k_4)$, based on the data above, what are all likely values of $k_2-k_1$, $k_3-k_1$, and $k_4-k_1$? Explain your answer.
\item  For what value(s) of $t$, would you expect $\mathrm{MutIndCo}(s^{(3)},E_t(s^{(4)}))$ to be large? Explain your answer.
\end{enumerate}\



\end{enumerate}

\end{document}
