 \documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm}
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amssymb,multicol}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{enumitem,systeme}
\usepackage{xcolor}

\newcommand{\Z}{\mathbb{Z}}
\newtheorem*{theorem}{Theorem}

\newlist{checklist}{itemize}{2}
\setlist[checklist]{label=$\square$}

\begin{document}
\begin{center}
{\Large Homework 5}\\
Due: Friday,  March 18 at noon\\


\end{center}
{\bf Instructions:} Submit a pdf of your solutions to the HW 5 assignment on Gradescope. 



\begin{enumerate}
\item[0.] If you would like any of these problems to be graded for proficiency with the core skills, list the skill and the corresponding problem. 
\item Solve each of the following simultaneous systems of congruences or explain
why no solution exists.
\begin{enumerate}
\item $\systeme*{x\equiv 5\pmod{13}, x\equiv 2\pmod{7}\;\;, x\equiv 4 \pmod{11}}$
\item $\systeme*{x\equiv 3\pmod{9}, x\equiv 2\pmod 6, x\equiv 1\pmod{5}}$
\end{enumerate}
(Note: this problem is worth 8 points--4 for each part)
   
\item Find three distinct (modulo 105) solutions to the equation $$x^2\equiv 4\pmod{105}.$$
\item This exercise will help us work towards understanding square roots. 
\begin{enumerate}
\item Let $p$ be a prime number, let $e\ge 1$ be an integer, and let $b$ be an integer such that $x^2\equiv b\pmod{p}$ has a solution.  Show that,  if $a_1$ and $a_2$ are two such solutions, then $a_1\equiv a_2\pmod{p}$ or $a_1\equiv -a_2\pmod{p}$. 
\item Provide a counterexample to show that the above statement is not necessarily true if $p$ is not prime. In other words, provide integers $m$, $b$, $a_1$, and $a_2$ such that $a_1^2\equiv b\pmod{m}$, $a_2^2\equiv b\pmod{m}$, but $a_1\not \equiv \pm a_2 \pmod{m}$. Make sure you explain why your counterexample is, in fact, a counterexample. 
\end{enumerate}
(Note: This problem is worth 7 points--4 for part a, and 3 for part b.)
\item Prove or disprove:\\ For any positive integers $m$ and $n$,  and any integers $a$ and $b$, the system of equations $$\systeme*{x\equiv a\pmod{m},  x\equiv b\pmod{n}\;}$$
  will have at least one solution. 
\end{enumerate}
\end{document}