   \documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{xcolor}

\newcommand{\Z}{\mathbb{Z}}
\begin{document}
\begin{center}
{\Large Homework 1}\\
Due: Friday September 16, 2021\\


\end{center}
{\bf Instructions:} Submit a pdf of your solutions to the HW 1 Computational assignment on Canvas. Remember that your work will be graded based on how well it meets \href{https://docs.google.com/document/d/1emM06_WRh_h941rsjtRE9fRVndJtfRKd9gyS3Fs_rFA/edit?usp=sharing}{the specifications. }

\begin{enumerate}
\item Compute the following reductions.  Explain your steps. 
\begin{enumerate}
\item $-1000 \% 88$
\item $110\cdot 124 \% 3$
\item $5^{72} \% 13$
\end{enumerate}
\item Suppose you know that the plaintext ``math" has been encoded to the ciphertext ``HVOC" using a shift cipher.  You intercept the ciphertext ``DN API," which you know has been encoded with the same shift cipher.  Decrypt the entire message ``HVOC DN API." Make sure to show your work.   Is the attack you performed as part of this problem a chosen plaintext attack, a known plaintext attack, a brute force attack, or some other kind of attack?
\item Fix an integer $N$ so that $N\%16 = 3$.  What is $N\%4$?  Explain your answer.
\end{enumerate}
\end{document}