   \documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amssymb,systeme}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{xcolor}

\newcommand{\Z}{\mathbb{Z}}
\newcommand{\ds}{\displaystyle}
\begin{document}
\begin{center}
{\Large Homework 8: Computations}\\
Due: Friday November 19, 2021 at Noon\\


\end{center}
{\bf Instructions:} Submit a pdf of your solutions to the HW 8 Computational assignment on Canvas. Remember that your work will be graded based on how well it meets \href{https://docs.google.com/document/d/1emM06_WRh_h941rsjtRE9fRVndJtfRKd9gyS3Fs_rFA/edit?usp=sharing}{the specifications. }


\begin{enumerate}
 \item For the following values of $y$ and $p$, determine whether or not $y$ is a square modulo $p$ without using Euler's criterion.  If it is a square, find the principal square root of $y$ modulo $p$. (Note that, if you determine that $y$ is not a square modulo $p$, you must give a thorough explanation/proof why, even though this is a computational assignment.) \begin{enumerate}
\item $y=7$, $p=11$
\item $y=7$, $p=19$
 \end{enumerate}


\item  Bob and Alice would like to use the Diffie-Hellman Key Exchange to agree on a session key $k$. Alice and Bob agree on the prime $6829$ and that the base $6$ modulo $6829$. Alice chooses a secret random number $x$ and tells Bob that $6^x\%6829$ is $5792$. Bob chooses $3$ as his secret exponent. 
\begin{enumerate}
\item What is the shared secret key $k$ that Alice and Bob will be using?
\item You are able to gain access to the network Alice and Bob are using to communicate, so you decide to implement ain interceptor attack with exponent $c=15$. What key does Bob think he and Alice agreed to? What key does Alice think they agreed to?
\end{enumerate}	
\item Bruce would like to send Ada a message using her ElGamal cipher.  The public information that Ada has posted is that her prime modulus is $p = 157$, her primitive root modulo $157$ is $g = 5$, and (in the notation from lecture) she has computed $A = 91$.  Bruce's message for Ada is the plaintext $m = 121$, and his secret exponent is $k = 14$.  What information should Bruce send to Ana in order to communicate the message $m = 121$ through her ElGmal cipher?  
\end{enumerate}
\end{document}
