   \documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm}
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amssymb,multicol}
\usepackage{hyperref, enumitem}
\usepackage{xcolor}

\newcommand{\Z}{\mathbb{Z}}
\newtheorem*{theorem}{Theorem}

\newlist{checklist}{itemize}{2}
\setlist[checklist]{label=$\square$}

\begin{document}
\begin{center}
{\Large Homework 1}\\
Due: Friday,  January 28 at noon\\


\end{center}
{\bf Instructions:} Submit a pdf of your solutions to the HW 1 assignment on Gradescope. 

When working on this assignment, you should focus on the following goals:
\begin{itemize}
\item Demonstrate that you understand the definition of reduction modulo $m$ and how it relates to the division algorithm. 
\item Clearly communicate computational solutions using complete sentences and enough explanation that another 5248 student could follow your work.
\item Clearly and correctly apply the definition of divisibility in a proof. 
\item Clearly and correctly apply the division algorithm in a proof.
\item Write clear and correct proofs that meet the following conventions of a mathematical proof:
\begin{checklist}
\item Written in complete sentences.
\item All assumptions stated at the beginning of the proof.
\item Define variables before/when you use them.
\item Use symbols when writing a precise mathematical formula or equation and English words when not writing a formula (i.e. do not use a symbol, such as $\forall,\, \exists,\, \therefore, \, \implies$ in place of a word). 
\item Show computational/algebraic work vertically and centered in the page. 
\end{checklist}
\end{itemize}

\begin{enumerate}
\item[0.] If you would like any of these problems to be graded for proficiency with the core skills, list the skill and the corresponding problem.
\item Compute the following reductions.  Explain your steps.  For parts (b) and (c), show your work without using any integers larger than 144. 
\begin{multicols}{3}
\begin{enumerate}
\item $(-1000) \% 88$
\item $(110\cdot 124) \% 3$ 
\item $\left(5^{72}\right) \% 13$ 
$144$.)
\end{enumerate}
\end{multicols}
\item Suppose you know that the plaintext ``math" has been encoded to the ciphertext ``HVOC" using a shift cipher.  You intercept the ciphertext ``DN API," which you know has been encoded with the same shift cipher.  Decrypt the entire message ``HVOC DN API." Make sure to show your work.   What type of attack did you perform?
\item Fix an integer $N$ so that $N\%16 = 3$.  What is $N\%4$?  Explain your answer. (Note that you want to show that your answer works for any integer $N$ such that $N\%16=3$.)

\item Fix an integer $N$ such that $N\%4=3$. What are the possible values of $N\%16$?

\item Let $a$, $b$, and $c$ be integers such that $a|b$ and $a|c$. Prove that,  for any integers $u$ and $v$, $a|ub+vc$. 

\item Let $m$ be any positive integer. Prove that  if $r$ is the reduction of $N$ modulo $m$ with $r\ne 0$, then $m-r$ is the reduction of $-N$ modulo $m$. (Hint: the reduction modulo $m$ is the same as the unique remainder given by the division algorithm.)

\end{enumerate}

\end{document}
