   \documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm}
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{amssymb,multicol}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{enumitem}
\usepackage{xcolor,systeme}

\newcommand{\Z}{\mathbb{Z}}
\newtheorem*{theorem}{Theorem}
\newtheorem*{lemma}{Lemma}

\newlist{checklist}{itemize}{2}
\setlist[checklist]{label=$\square$}

\begin{document}
\begin{center}
{\Large Homework 5}\\
Due: Friday,  March 1 at noon\\


\end{center}
{\bf Instructions:} Submit a pdf of your solutions to the HW 5 assignment on Gradescope.  {\bf You must complete the process by associating the proper page(s) to each question.} (If you fail to do so, you may earn ``not assessable" on any problems that do not have solutions matched to them.)\\[3pt]

\noindent When working on this assignment, you should focus on the following goals:
\begin{itemize}
\item Demonstrate understanding of solving systems of equations and/or showing that a system of equations has no solutions.
\item Demonstrate understanding of the Hill Cipher. 
\item Demonstrate understanding of Bezout's identity by using it clearly and correctly in a proof. 
\item Write a clear and correct proof by induction. 
\end{itemize}

\begin{enumerate}
 \item  A friend sends you the encrypted message $ET$ using a Hill cipher whose key you and your friend agreed at a previous meeting would be $K = \begin{pmatrix}
6 & 7\\ 
11 & 5
\end{pmatrix}$.  What is the plaintext of the message your friend sent you?\\

\item Solve the following simultaneous system of congruences or explain why no solution exists.(Note that your final answer should be of the form $x\equiv a\pmod{m}$ for appropriate choices of $a$ and $m$.)
$$\systeme*{x\equiv 5\pmod{13}, x\equiv 2\pmod{7}\;\;, x\equiv 4 \pmod{11}}$$

\item Solve each of the following simultaneous system of congruences or explain why no solution exists. (Note that your final answers should be of the form $x\equiv a\pmod{m}$ for appropriate choices of $a$ and $m$.)
\begin{enumerate}
\item $\systeme*{x\equiv 3\pmod{9}, x\equiv 2\pmod 6, x\equiv 1\pmod{5}}$
\item $\systeme*{x\equiv 5\pmod{9}, x\equiv 2\pmod 6, x\equiv 1\pmod{5}}$
\end{enumerate}
\item This problem will complete the proof of the CRT by helping you prove the important lemma we used without proof in class.
\begin{enumerate}
\item Prove that, if $a$ and $b$ are coprime integers and $a,b|c$, then $ab|c$. (Hint: Use Bezout's identity.)
\item Using induction with part (a) as the base case, prove the following lemma.
\begin{lemma} If $a_1,a_2,\ldots, a_k|c$ and $a_1,a_2,\ldots, a_k$ are pairwise coprime, then $a_1a_2\cdots a_k|c$. 
\end{lemma}
(Remark: You may cite the result of part a in your proof of part b.)
\end{enumerate}

\end{enumerate}

\end{document}